Missing The Point

### 2020-09-18 Manuscript.Rmd
Edit abstract

# Missing The Point

@@

>>>>

# Missing The Point: Non-Convergence in Iterative Imputation Algorithms

## Abstract

Iterative imputation is a popular tool to accommodate the ubiquitous problem of missing data. While it is widely accepted that this technique can yield valid inferences, these inferences all rely on algorithmic convergence. Our study provides insight into identifying non-convergence in iterative imputation algorithms, since there is no consensus on how to evaluate the convergence properties currently. We found that--in the cases considered--inferential validity was achieved after five to ten iterations, much earlier than indicated by diagnostic methods. We conclude that it never hurts to iterate longer, but such calculations hardly bring added value.

@@

Missing data poses a ubiquitous threat against unbiased, confidence-valid statistical inferences. A popular tool to accommodate missing data. With techniques like multiple imputation (Rubin, 1987), missing data points are imputed (i.e., 'filled in')
